\section*{Education}

\noindent \textbf{UNSW Sydney} | \textit{PhD in Information Systems}
\\ 2018 to 2021 (expected)
\begin{myitemize}
	\item Funded by the Australian Government Research Training Program (RTP) Scholarship and the UNSW Business School Supplementary Scholarship.
	\item Researching digital work and digital nomads.
	\item Supervised by Prof. Dubravka Cecez-Kecmanovic, Associate Prof. Daniel Schlagwein \textit{(Sydney University, external)}, and Dr. Michael Cahalane.
	\item Developed \textit{\href{http://litbaskets.io/}{litbaskets}}, a web app that assists with literature search via Scopus.
\end{myitemize}

\vspace{20pt}

\noindent \textbf{Massive online open courses} | \textit{Continual self-study}
\\ 2016 onwards
\begin{myitemize}
	\item Foundations of Marketing Analytics, via Coursera, ESSEC Business School. Completed December 2016. Certificate \texttt{\href{https://www.coursera.org/account/accomplishments/certificate/FB9K6N8V7N8N}{FB9K6N8V7N8N}}.
	\item Introduction to Big Data, via Coursera, University of California San Diego (UCSD). Completed February 2016. Certificate \texttt{\href{https://www.coursera.org/account/accomplishments/certificate/DGRM53TG8T4H}{DGRM53TG8T4H}}.
	\item Introduction to Python for Data Science, via edX, Microsoft. Completed February 2016. Certificate \texttt{\href{https://courses.edx.org/certificates/90a167cdacda404d8688db9092c07972}{90a167cdacda404d8688db9092c07972}}.
\end{myitemize}

\pagebreak

\noindent \textbf{UNSW Sydney} | \textit{Bachelor of Information Systems (Co-op, Honours)}
\\ 2012 to 2016
\begin{myitemize}
	\item Honours research: Persuasive Crowdfunding Platform Design.
	\item Developed \textit{\href{https://github.com/blairw/litfam}{litfam}}, software that assists with literature review and citation mapping.
\end{myitemize}

\vspace{20pt}

\noindent \textbf{James Ruse Agricultural High School}
\\ 2006 to 2011
\begin{myitemize}
	\item Australian Tertiary Admissions Rank (ATAR) of \texttt{99.55}.
\end{myitemize}