\section*{Employment}

\noindent \textbf{UNSW Sydney} | \textit{Casual Academic Staff}
\\ July 2018 onwards
\begin{myitemize}
	\item Tutor for \texttt{INFS1609} (Fundamentals of Business Programming).
	\item Tutor for \texttt{INFS3617} (Networking \& Cyber Security).
\end{myitemize}

\vspace{20pt}

\noindent \textbf{Connections Australia} | \textit{Software Engineer}
\\ July 2017 to June 2018
\begin{myitemize}
	\item Data ETL of ABS Census 2016 data using Python, and then geospatial visualisation using JavaScript, jQuery, mySQL, and PHP.
	\item Migration of legacy iOS codebase to Swift 4 + Cocoapods.
	\item Hands-on experience with .NET Entity Framework for a web API.
	\item Enhanced familiarity with Grav CMS, Twig templating, Bulma, and GitHub.
\end{myitemize}

\vspace{20pt}

\noindent \textbf{Datorama Australia} | \textit{Client Success Executive}
\\ October 2016 to June 2017
\begin{myitemize}
	\item Advised customers of a specialised cloud-based analytics software solution.
	\item \href{https://datorama.com/blog/2017/06/28/datorama-tips-tricks-custom-visualizations-d3-js/}{Bespoke development of data visualisations} using open source libraries.
	\item Enhanced familiarity with digital advertising and marketing strategy.
\end{myitemize}

\vspace{20pt}

\noindent \textbf{IBM Global Business Services} | \textit{Technical Consultant}
\\ January to September, 2016
\begin{myitemize}
	\item Server management with WebSphere and Red Hat Enterprise Linux.
	\item Support lifecycle and dev ops, ticketing through JIRA and BMC Remedy.
	\item Enhanced understanding of Adaptive Case Management and Cybersecurity.
\end{myitemize}

\vspace{20pt}

\noindent \textbf{UNSW Sydney} | \textit{Casual Academic Staff}
\\ January to December, 2016
\begin{myitemize}
	\item Peer Assisted Study Session (PASS) facilitator for \texttt{INFS1602} (Digital Transformation in Business), \texttt{INFS1603} (Introduction to Business Databases), and \texttt{INFS1609} (Fundamentals of Business Programming).
	\item Exam grader.
\end{myitemize}

\vspace{20pt}

\noindent \textbf{IBM Global Business Services} | \textit{Intern Consultant}
\\ July 2014 to January 2015

\vspace{20pt}

\noindent \textbf{American Express Technologies} | \textit{Intern Business Analyst}
\\ January to June, 2014

\vspace{20pt}

\noindent \textbf{Origin Energy} Project Management Office | \textit{Intern Analyst}
\\ January to June, 2014

\vspace{20pt}